Self Regulation Ontology Retest Data Report

### 2017-04-23 SRO_Report.Rmd
added quick script for bootstrapping for sherlock

```{r eval=FALSE, echo=FALSE}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  if('icc' %in% metric){
    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('spearman' %in% metric){
    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('eta_sq' %in% metric){
    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('sem' %in% metric){
    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  return(out_df)
}

bootstrap_relialibility(dv_var = numeric_cols[1])

>>>>

```{r}
sample_workers = function(N = 150, repl= TRUE, df=retest_data, worker_col = "sub_id"){
  return(sample(df[,worker_col], N, replace = repl))
}

bootstrap_relialibility = function(metric = c('icc', 'spearman', 'eta_sq', 'sem'), dv_var){
  tmp_sample = sample_workers()
  out_df = data.frame(dv = dv_var)
  if('icc' %in% metric){
    out_df$icc = get_icc(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('spearman' %in% metric){
    out_df$spearman = get_spearman(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('eta_sq' %in% metric){
    out_df$eta_sq = get_eta(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  if('sem' %in% metric){
    out_df$sem = get_sem(dv_var, sample = 'bootstrap', sample_vec = tmp_sample)
  }
  return(out_df)
}
```

Bootstrapping everything at once locally would take around four hours.
```{r eval=FALSE}
as.data.frame(numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  # rowwise()%>% #this works too but the output is nicer the other way
  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))
